Reproducibility in plant pathology: where do we stand and a way forward

### 2021-06-22 analysis/paper/paper.Rmd
Insert missing "but" on line 153
Wordsmithing on line 153
Update Kaique's middle initial per his preferences

---
title: "Reproducibility in plant pathology: where do we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Kaique dos Santos Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/template.docx" # Insert path for the DOCX file
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
---

@@

It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility. 
However, very often biological specimens such as strains, cultures or cultivars are often not available. 
These cases of a lack of reproducibility will not be covered here.

>>>>

---
title: "Reproducibility in plant pathology: where do we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Kaique S. Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/template.docx" # Insert path for the DOCX file
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
---

@@

It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility. 
However, very often biological specimens such as strains, cultures or cultivars are often not available. 
These cases constitute a lack of a lack of reproducibility but will not be covered here.
